### 2016-07-17 appendix.tex
Testing procedure. BusyBox wget command fails when testing remote booting

\subsection{Paramiko Package Update}
\label{sec:paramiko}
In case Paramiko version 1.15.1 or higher is not installed, we may observe
a key exchange algorithm error. In this case, it might be
necessary to update the Paramiko package and verify this by running:

>>>>

\subsection{Paramiko Package Update}
\label{sec:paramiko}
In case Paramiko version 1.15.1 or higher is not installed, we may observe
a key exchange algorithm error when trying to log in through \ac{SSH} to a
Raspi. In this case, it might be necessary to update the Paramiko package
that Fabric uses for this purpose and verify this by running:
